\documentclass[a4paper]{article}
\usepackage[margin=1in]{geometry} 
% \usepackage{ctex}
%\usepackage{tabularx}
%\usepackage{lipsum}
\usepackage{enumerate}
%\usepackage{apacite}
%\usepackage{amsfonts}
%\usepackage{multirow}
\usepackage{cite}
\usepackage{apacite}
\usepackage{titlesec}
\usepackage{color}
% \usepackage[number, sort&compress]{natbib}

\title{\textbf{Importance of academic writing skills}}
% \author{Eric Zhou}
% \date{\today}
\titleformat{\section}[block]{\Large\bfseries\filcenter}{}{1em}{}
\begin{document}
\maketitle

\section{Original version}

Academic writing skills are very important since they can help us in many aspects. Not only can they ensure our academic integrity, which plays a vital role in our all-round development, but also they can help those who want to read our articles understand our ideas better. What's more, academic writing is a necessary part in our Internal Assesments, Extended Essay as well as our future university lives. There for it's of great signifigance for us to learn how to correctly write articles in an academic context.

\section{Enhanced version}

Academic writing skills are very important since they can help us in many aspects. Not only can they ensure our academic integrity, which plays a vital role in our all-round development, but also they can help those who want to read our articles understand our ideas better. What's more, academic writing is a necessary part of our Internal Assessments, Extended Essays, and our future university lives. Therefore it is of great significance for us to learn how to correctly write articles in an academic context.

\section{Acknowledgements}

Grammarly is used to enhance this passage.

%\centering

\section{References}

\newcommand*{\dif}{\mathop{}\!\mathrm{d}}

% OpenAI. (2024). ChatGPT. (Version GPT3.5). [Large Language Model]. \textcolor{blue}{https://openai.com/chatgpt/} 
% $ \sum_{i=0}^{10}\int_{0}^{\pi}{{\sin(x^{(3)})}\over{\arcsin({x^2}\theta_i)}}\dif x $

Grammarly Inc. (2024). Grammarly. [Writing Assistant]. \color{blue}{https://app.grammarly.com/}.

%\bibliographystyle{apacite}
% \raggedleft
%\bibliography{.\\cit.bib}

\end{document}