\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{datetime}
\usepackage{tcolorbox}

% Custom colors for different speakers
\definecolor{modcolor}{RGB}{0,0,128}       % Moderator - Navy Blue
\definecolor{affirmcolor}{RGB}{0,100,0}    % Affirmative - Dark Green
\definecolor{negcolor}{RGB}{139,0,0}       % Negative - Dark Red

% Page setup
\geometry{a4paper, margin=1in}
\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{gray}{Debate Title Here}}
\lfoot{\textcolor{gray}{\today}}
\rfoot{\textcolor{gray}{Page \thepage}}

% Custom commands
\newcommand{\moderator}[1]{{\color{modcolor}\textbf{Moderator:} #1}}
\newcommand{\affirmative}[1]{{\color{affirmcolor}\textbf{Affirmative:} #1}}
\newcommand{\negative}[1]{{\color{negcolor}\textbf{Negative:} #1}}
\newcommand{\timestamp}{{\color{gray}\scriptsize[\currenttime]}}

\begin{document}

\title{\Huge \textbf{TOK Debate Recording}}
\author{Can we apply the same ethical standards to everyone?}
\date{\today}
\maketitle

\section*{Participants}
\begin{description}
    \item[Moderators:] Louis, Eric, Moira, Lilian.
    \item[Affirmative Team:] Alex, Sofia, Felicia, Bonnie.
    \item[Negative Team:] Hank, Wendy, Bettie, Scarlett.
\end{description}



\section*{Debate}

%\subsection*{1. Introduction}
%\moderator{Welcome to today's debate on whether we can apply the same ethical standards to everyone.. 
%Alex, Sofia, Felicia and Bonnie are the affirmative team -- universalists. Hank, Wendy, Bettie and Scarlett are the negative team -- relativism. \timestamp}


\begin{tcolorbox}[title = Note]
    The moderator note goes here.
\end{tcolorbox}

%\subsubsection*{Affirmative Team (7 minutes)}
\affirmative{Alex:
\begin{enumerate}
    \item Moral system can be presented to all humans. 
    \item Human right ethical system by the UN is a widely accepted moral system.
\end{enumerate}}

\affirmative{Bonnie:
\begin{enumerate}
    \item Not everyone agree on each other but it (the universal moral standard) exists.
    \item Care for infants, Red Cross Organizations, Ethical and empathy are the examples.
\end{enumerate}}

\begin{tcolorbox}[title = Note on affirmative team]
    The team has provided their opinions with serveral convincing instances, which is fine. However, as the beginning debater, they seem to forget to define the term 'universal' and 'ethics', which should play a role in later discussion. It is in this way that they lost their advantage of speaking the first.
\end{tcolorbox}

\negative{Scarlett:
\begin{enumerate}
    \item Moral behaviour may harm others. 
    \item Different culture or society. 
    \item India: arranged marrige in India vs US and CHN 
    \item More prople accept GPT, different time.
    \item Only some country allow painless death. Some country have death penalty. This law is an extension on ethics.
\end{enumerate}}

\affirmative{Bonnie and Alex
    \begin{enumerate}
        \item Difference in law to painless death not equal to different ethic standards.
        \item Difference in culture does not mean the ethic standards are different.
    \end{enumerate}
}

\begin{tcolorbox}[title = Note on both teams]
    Although those arguments might sound convincing, the reasoning is lacking. For example, why is marrige a representation of the moral system, not the economical status or the religon? The affirmative team seems to found the point, but they did not express themselves clearly enough and raise questions back, making Hank have the ability to elaborate on Anlesi (euthanasia).
\end{tcolorbox}

\negative{Hank
\begin{enumerate}
    \item US individual freedom over social responsibility, so ok for painless death. CHN social responsibility over freedom, so the opposite.
    \item Killing is immoral. But no actual reasoning to prove that.
\end{enumerate}
}

\negative{Wendy
\begin{enumerate}
    \item Human right widely accepted, but different definition.
\end{enumerate}
}

\begin{tcolorbox}[title = Note on negative team]
    Those two examples (murder and human right) sound risky. The opponents may use these as examples to say that they actually prove their opinions. For example, the fact that murder is bad and human right is good are the same. People have the same goals, just the way is the different. But they managed to get it through.
\end{tcolorbox}

\affirmative{Alex
\begin{enumerate}
    \item ?
\end{enumerate}
}

\begin{tcolorbox}[title = Note]
    Nothing meaningful was heard clearly. It seems none of other judges did.
\end{tcolorbox}

\negative{Scarlett
\begin{enumerate}
    \item Some areas (), avenging a family member is encouraged, but in China it is illegal.
\end{enumerate}
}

\begin{tcolorbox}[title = Note on negative team]
    A lacking for specific example in the braces. Perhaps contrasting the ancient times and modern times may sound more authentic. This argument can also be denied using the note above.
\end{tcolorbox}

\affirmative{Bonnie
\begin{enumerate}
    \item Some ethics is universal, some is not. A counter example is not sufficient. (not clearly delivered)
    \item 90 precent agree is enough to say that is universal.
\end{enumerate}
}

\negative{Hank
\begin{enumerate}
    \item 90 percent make the debate meaningless.
    \item Slavery used to be common, but it is not ethical now. 
    \item Was it moral (Bonnie: yes)
    \item Why is there civil war in the US? (Bonnie: they were all persuing the better life in different ways.)
    \item School shooting is unethical, persuing the better life.
\end{enumerate}
}

\begin{tcolorbox}[title = Note]
    It seems Hank and Bonnie has been speaking too much. 
    Some ideas are not delivered clearly. 
    Bonnie could have said that the purpose, or the ethical drive of the both side in civil war are the same. But she didn't say so.
\end{tcolorbox}

\negative{Bettie
\begin{enumerate}
    \item Developed in different socio-economical context.
    \item Polygamy in Middle East vs US, EU, etc.
\end{enumerate}
}

\affirmative{Sofia
\begin{enumerate}
    \item However, betraying the spouse is unethical in all cultures.
\end{enumerate}
}

\affirmative{Felicia
\begin{enumerate}
    \item Slavery in EU and US was common, treatment to slaves are better than Chinese labor actually.
    \item Therefore slaves are actually employees, that does not make slavery unethical.
\end{enumerate}
}

\negative{Hank
\begin{enumerate}
    \item That means the ethical standards are not universal.
\end{enumerate}
}

\begin{tcolorbox}[title = Note]
    It seems that Felicia has been leading the team to an awkward situation. Some seemingly meaningless speech was not recorded. 
\end{tcolorbox}

\affirmative{Sofia
\begin{enumerate}
    \item Universal condamnent on slavery is also an instance for universal ethics.
\end{enumerate}
}

\negative{Wendy
\begin{enumerate}
    \item Personal experience and education, social education can shape one's ethic system.
\end{enumerate}
}

\affirmative{Bonnie
\begin{enumerate}
    \item 6-month kids can show some universal ethic of not hurting others? (Wendy, Bettie, Hank: not representative enough, some factors like family environment is not considered.)
\end{enumerate}
}

\section*{Overall comment} The two teams in this debate has delivered their opinions with many examples and some reasoning. However, there is a little lacking in collaboration in different group members (for example, some examples given by the negative team are actually proving the same point) and some counter-arguments did not target at the specific flaw in the opposing team's statement. 

\section*{Reference}

This template was generated by deepseek (\textit{generate a debate recording template in latex for me}). But all content was typed manually.

\end{document}