\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{datetime}

% Custom colors for different speakers
\definecolor{modcolor}{RGB}{0,0,128}       % Moderator - Navy Blue
\definecolor{affirmcolor}{RGB}{0,100,0}    % Affirmative - Dark Green
\definecolor{negcolor}{RGB}{139,0,0}       % Negative - Dark Red

% Page setup
\geometry{a4paper, margin=1in}
\pagestyle{fancy}
\fancyhf{}
\rhead{\textcolor{gray}{Debate Title Here}}
\lfoot{\textcolor{gray}{\today}}
\rfoot{\textcolor{gray}{Page \thepage}}

% Custom commands
\newcommand{\moderator}[1]{{\color{modcolor}\textbf{Moderator:} #1}}
\newcommand{\affirmative}[1]{{\color{affirmcolor}\textbf{Affirmative:} #1}}
\newcommand{\negative}[1]{{\color{negcolor}\textbf{Negative:} #1}}
\newcommand{\timestamp}{{\color{gray}\scriptsize[\currenttime]}}

\begin{document}

\title{\Huge \textbf{TOK Debate Recording}}
\author{Can we apply the same ethical standards to everyone?}
\date{\today}
\maketitle

\section*{Participants}
\begin{description}
    \item[Moderators:] Louis, Eric, Moira, Lilian.
    \item[Affirmative Team:] Alex, Sofia, Felicia, Bonnie.
    \item[Negative Team:] Hank, Wendy, Bettie, Scarlett.
\end{description}



\section*{Debate Structure}

\subsection*{1. Introduction}
\moderator{Welcome to today's debate on [Topic Here]. Today's motion is: \textit{"Insert Debate Motion Here"}. 
We have [Name1] and [Name2] representing the affirmative team, and [Name3] and [Name4] 
representing the negative team. \timestamp}

\subsection*{2. Opening Statements}

\subsubsection*{Affirmative Team (7 minutes)}
\affirmative{First speaker presents arguments:
\begin{enumerate}
    \item Main argument 1 \timestamp
    \item Main argument 2 \timestamp
    \item Main argument 3 \timestamp
\end{enumerate}}

\subsubsection*{Negative Team (7 minutes)}
\negative{First speaker presents arguments:
\begin{enumerate}
    \item Main argument 1 \timestamp
    \item Main argument 2 \timestamp
    \item Main argument 3 \timestamp
\end{enumerate}}

\subsection*{3. Rebuttals}

\subsubsection*{Affirmative Rebuttal (5 minutes)}
\affirmative{Response to negative arguments:
\begin{itemize}
    \item Counter-point 1 \timestamp
    \item Counter-point 2 \timestamp
\end{itemize}}

\subsubsection*{Negative Rebuttal (5 minutes)}
\negative{Response to affirmative arguments:
\begin{itemize}
    \item Counter-point 1 \timestamp
    \item Counter-point 2 \timestamp
\end{itemize}}

\subsection*{4. Cross-Examination}

\subsubsection*{Affirmative Questions Negative (3 minutes)}
\moderator{The floor is now open for cross-examination between teams \timestamp}

\subsubsection*{Negative Questions Affirmative (3 minutes)}
\moderator{Continued cross-examination period \timestamp}

\subsection*{5. Closing Statements}

\subsubsection*{Negative Team Summary (4 minutes)}
\negative{Final arguments summarizing position:
\begin{itemize}
    \item Key point 1 \timestamp
    \item Key point 2 \timestamp
\end{itemize}}

\subsubsection*{Affirmative Team Summary (4 minutes)}
\affirmative{Final arguments summarizing position:
\begin{itemize}
    \item Key point 1 \timestamp
    \item Key point 2 \timestamp
\end{itemize}}

\subsection*{6. Conclusion}
\moderator{Thank you to all participants. The judges will now deliberate. [Add any concluding remarks here.] \timestamp}

\section*{Reference}

This template was generated by deepseek (\textit{generate a debate recording template in latex for me}). But all content was typed manually.

\end{document}